Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-01-22 Paper/paper.tex
Whoops

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{BlockDiagram.pdf}
\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).  We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.  From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\sigma$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
\label{fig:ConceptFigure}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{BlockDiagram.pdf}
\caption{An block diagram of our technique, illustrated by a 1D periodic time series with additive Gaussian noise ($n_t \in \mathcal{N}(0, 1)$).  We estimate the period to be 24 (a multiple of the fundamental frequency), and perform a 24-length sliding window embedding.  From this, we use the mean of the birth and death time of the largest persistence dot to autotune the scale $\sigma$ for the graph Laplacian, from which we derive circular coordinates $\phi$, which can be used to reorder the sliding windows and use them to vote on a final slow motion template.}
\label{fig:ConceptFigure}
\end{figure*}
